\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Correct TDCN name
It should be TDCN and not TDCNN for Time-Dilated Convolutional Network (Network is already in the acronym!)

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcnn} (TDCNN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCNN++, was improved by \cite{tdcnnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcnn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

			TDCNN++ presents the interesting property of having almost the same architecture as TDCNN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data type used for training.

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				OpenUnmix & 24.48\\
				\hline
				TDCNN & 26.44\\
				\hline
				TDCNN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed.}
		\label{tab:distances}
	\end{table}

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations. TDCNN++, OpenUnmix, and NMF also performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

@@

	Furthermore, it seems that unsupervised methods such as NMF outperform all supervised methods. However, it is important to notice that the different neural models (Demucs, ConvTasNet, ConvTasNetUniversal and OpenUnmix) were used based on pre-trained versions. Those versions were trained on musical data, except for TDCNN++ which used selected generic sound samples, which opens a large path for improvement. More specifically, we may infer from our results that models trained not only on musical data can generate a better separation for orchestration, as TDCNN++ outperforms other supervised models.

>>>>

			\subsubsection{ConvTasNet}
			ConvTasNet \cite{tdcn} (TDCN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modelling sequential data, as series of dilateds convolutions are a good way to capture temporal patterns.

@@

			\subsubsection{Universal Sound Separation ConvTasNet}
			This version of ConvTasNet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affected the masking network. More specifically, feature-wise normalization replaces global normalization, residual connections ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data type used for training.

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				OpenUnmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed.}
		\label{tab:distances}
	\end{table}

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations. TDCN++, OpenUnmix, and NMF also performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

@@

	Furthermore, it seems that unsupervised methods such as NMF outperform all supervised methods. However, it is important to notice that the different neural models (Demucs, ConvTasNet, ConvTasNetUniversal and OpenUnmix) were used based on pre-trained versions. Those versions were trained on musical data, except for TDCN++ which used selected generic sound samples, which opens a large path for improvement. More specifically, we may infer from our results that models trained not only on musical data can generate a better separation for orchestration, as TDCN++ outperforms other supervised models.
